Lesson 4
========================================================

***

### Scatterplots and Perceived Audience Size
Notes:

***

### Scatterplots
Notes:

```{r Scatterplots}
encoding = "UTF-8"
library(ggplot2)
getwd()  #默认打开文件的 那个地方就是工作区了，原来如此。
# ssetwd("D:\存放东西的仓库\Python开源或者是别的东西\数据分析\项目三_探索性数据分析EDA\课程5，双变量分析")   斜杠是反向的才对
pf <-read.delim('pseudo_facebook.tsv')
# pf <- read.csv("")
ggplot(data=pf,aes(x=pf$age,y=pf$friend_count))+geom_point()
#点数输出来了，但是其实堆叠起来后看不清楚到底多还是少。所以就需要调节
```

***

#### What are some things that you notice right away?
Response:
很多的点都杂糅在一起了，其实看不清到底下面那一片之间那儿密集一点，都看不清额
***

### ggplot Syntax
Notes:

```{r ggplot Syntax}
pfplot <- ggplot(data=pf,aes(x=pf$age,y=pf$friend_count))
#设置透明度，这个是防止点给遮挡了。但是下面部分好像还是存在看不清的情况，所以这时候就需要“抖动”
pfplot+geom_point(alpha=1/20)
pfplot+geom_point(alpha=1/20,position=position_jitter(height =0))


```

***

### Overplotting
Notes:

```{r Overplotting}

```

#### What do you notice in the plot?
Response:

***

### Coord_trans()
Notes:

```{r Coord_trans()}
pfplot+geom_point(alpha=1/20,position=position_jitter(height =0))+xlim(10,60)  
#这个是使用限制显示x轴的。

pfplot+geom_point(alpha=1/20,position=position_jitter(height =0))+xlim(10,60)+coord_trans(y='sqrt')      #这个是开方后的。让y轴开方



```

#### Look up the documentation for coord_trans() and add a layer to the plot that transforms friend_count using the square root function. Create your plot!

```{r}

```

#### What do you notice?

***

### Alpha and Jitter
Notes:

```{r Alpha and Jitter}
pfplot+geom_point(alpha=1/20,position=position_jitter(height =0))+xlim(10,60)+coord_trans(y='sqrt')  
```

***

### Overplotting and Domain Knowledge
Notes:

***

### Conditional Means
Notes:
增加数据框的均值来进行处理，这个东西不可以太慢了。
为了了解变量的平均值或者中位数 才能更好的看到变量之间的关系
```{r Conditional Means}  
install.packages('dplyr')
library(dplyr)

#第一种情况，不适用dplyr包
age_group <- group_by(pf,age)
pf.fc_by_age <-summary(age_group,
        friend_count_mean=mean(friend_count),
        friend_count_median = median(friend_count),
        n = n())
pf.fc_by_age <- arrange(pf.fc_by_age,age)
head(ppf.fc_by_age)

# 上面第一种报错了，现在这儿开始时第二种方法
pf.fc_by_age <-pf %>%
  group_by(age) %>%
  summarise(friend_count_mean = mean(friend_count),
            friend_count_median = median(friend_count),
            n = n() ) %>%
  arrange(age)

head(pf.fc_by_age)

ggplot(data = pf,aes(x = pf.fc_by_age))+geom_point()
```

Create your plot!

```{r Conditional Means Plot}

```

***

### Overlaying Summaries with Raw Data
Notes:

```{r Overlaying Summaries with Raw Data}

```

#### What are some of your observations of the plot?
Response:

***

### Moira: Histogram Summary and Scatterplot
See the Instructor Notes of this video to download Moira's paper on perceived audience size and to see the final plot.

Notes:

***

### Correlation
Notes:

```{r Correlation}

```

Look up the documentation for the cor.test function.

What's the correlation between age and friend count? Round to three decimal places.
Response:

***

### Correlation on Subsets
Notes:

```{r Correlation on Subsets}
with(                 , cor.test(age, friend_count))
```

***

### Correlation Methods
Notes:

***

## Create Scatterplots
Notes:

```{r}

```

***

### Strong Correlations
Notes:

```{r Strong Correlations}

```

What's the correlation betwen the two variables? Include the top 5% of values for the variable in the calculation and round to 3 decimal places.

```{r Correlation Calcuation}

```

Response:

***

### Moira on Correlation
Notes:

***

### More Caution with Correlation
Notes:

```{r More Caution With Correlation}
install.packages('alr3')
library(alr3)
```

Create your plot!

```{r Temp vs Month}

```

***

### Noisy Scatterplots
a. Take a guess for the correlation coefficient for the scatterplot.

b. What is the actual correlation of the two variables?
(Round to the thousandths place)

```{r Noisy Scatterplots}

```

***

### Making Sense of Data
Notes:

```{r Making Sense of Data}

```

***

### A New Perspective

What do you notice?
Response:

Watch the solution video and check out the Instructor Notes!
Notes:

***

### Understanding Noise: Age to Age Months
Notes:

```{r Understanding Noise: Age to Age Months}

```

***

### Age with Months Means

```{r Age with Months Means}

```

Programming Assignment
```{r Programming Assignment}

```

***

### Noise in Conditional Means

```{r Noise in Conditional Means}

```

***

### Smoothing Conditional Means
Notes:

```{r Smoothing Conditional Means}

```

***

### Which Plot to Choose?
Notes:

***

### Analyzing Two Variables
Reflection:

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!
```{r}
#探索两个变量的，data 。 price和x
library(ggplot2)
library(diam)


```
