Lesson 6
========================================================

### Welcome
Notes:
# 失恋和白白双重打击把。
1.复习散点图，y=price ，x weight
***

### Scatterplot Review
```{r}
library(ggplot2)
library(reshape2)

```

```{r Scatterplot Review}
ggplot(subset(diamonds,price <= quantile(price,0.1)),aes(x=carat,y=price))+geom_point()


#没加特效时候的答案
ggplot(diamonds,aes(x=carat,y=price))+
  xlim(0,quantile(diamonds$carat,0.99))+
  ylim(0,quantile(diamonds$price,0.99))+
  geom_point()


#加特效后的答案，更容易识别和看
ggplot(diamonds,aes(x=carat,y=price))+
  xlim(0,quantile(diamonds$carat,0.99))+
  ylim(0,quantile(diamonds$price,0.99))+
  geom_point(fill=I("#F79420"),color=I("black"),shape=21)

```

***

### Price and Carat Relationship
Response:

***
```{r}

#加特效后的答案，更容易识别和看
ggplot(diamonds,aes(x=carat,y=price))+
  xlim(0,quantile(diamonds$carat,0.99))+
  ylim(0,quantile(diamonds$price,0.99))+
  geom_point(fill=I("#F79420"),color=I("black"),shape=21)+
  geom_smooth(method="lm")

# 图片可以看出，这种直献是无法合理的预测到图形的，会错过这个模型的一些东西，这个就叫做欠拟合。


```

### Frances Gerety
Notes:

#### A diamonds is


***

### The Rise of Diamonds
Notes:   钻石骗局


***

### ggpairs Function
Notes:

```{r ggpairs Function}
# install these if necessary
# install.packages('GGally')
# install.packages('scales')
# install.packages('memisc')
# install.packages('lattice')
# install.packages('MASS')
# install.packages('car')
# install.packages('reshape2')
# install.packages('plyr')

# load the ggplot graphics package and the others
library(ggplot2)
library(GGally)
library(scales)
library(memisc)

# sample 10,000 diamonds from the data set
set.seed(20022012)
# diamond_samp <- diamonds[sample(1:length(diamonds$price), 10000), ]
# ggpairs(diamond_samp, params = c(shape = I('.'), outlier.shape = I('.')))   zhege haoxiang yongbuliao 

ggpairs(diamond_samp, 
  lower = list(continuous = wrap("points", shape = I('.'))), 
  upper = list(combo = wrap("box", outlier.shape = I('.'))))


```

What are some things you notice in the ggpairs output?
Response:

***

### The Demand of Diamonds
Notes:

```{r The Demand of Diamonds}
library(gridExtra)

plot1 <- ggplot(data=diamonds,aes(x =price)) +geom_histogram() 
  # ggtitle('Price')

plot2 <- ggplot(data=diamonds,aes(x =price)) +geom_histogram(fill="yellow")+ scale_x_log10()  #使用对数标度
  # ggtitle('Price (log10)')

grid.arrange(plot1,plot2)

# 偏锋变成了双峰的图案。,对数转换，对数转换的作用是什么。
# 数据转换是一种处理偏态数据的方法
```

***

### Connecting Demand and Price Distributions
Notes:

***

### Scatterplot Transformation

```{r Scatterplot Transformation}

```


### Create a new function to transform the carat variable

```{r cuberoot transformation}
cuberoot_trans = function() trans_new('cuberoot', transform = function(x) x^(1/3),
                                      inverse = function(x) x^3)
```

#### Use the cuberoot_trans function
# 第10 讲到函数了，函数的这儿R中的，可以使用。
散点图转换，这儿使用
```{r Use cuberoot_trans}
ggplot(aes(carat, price), data = diamonds) + 
  geom_point() + 
  scale_x_continuous(trans = cuberoot_trans(), limits = c(0.2, 3),
                     breaks = c(0.2, 0.5, 1, 2, 3)) + 
  scale_y_continuous(trans = log10_trans(), limits = c(350, 15000),
                     breaks = c(350, 1000, 5000, 10000, 15000)) +
  ggtitle('Price (log10) by Cube-Root of Carat')
```

***

### Overplotting Revisited

第11题在这儿放着，

提示 1：在文档中查找 geom_point()。

提示 2：你需要为 geom_point() 中的 alpha、size 和 position 调整参数。

提示 3：要抖动散点，请将 position 设置为等于“jitter”。
```{r Sort and Head Tables}
#  size 说的是半径为1的圆嘛

ggplot(aes(carat, price), data = diamonds) + 
  geom_point(alpha=0.5,size=3/4,position = position_jitter(width = 0.5,height = 0)) + 
  scale_x_continuous(trans = cuberoot_trans(), limits = c(0.2, 3),
                     breaks = c(0.2, 0.5, 1, 2, 3)) + 
  scale_y_continuous(trans = log10_trans(), limits = c(350, 15000),
                     breaks = c(350, 1000, 5000, 10000, 15000)) +
  ggtitle('Price (log10) by Cube-Root of Carat')

# 答案 ,position =jitter 就这样放在这儿了。这个是默认的处理方法，可以在不清楚参数时候使用
ggplot(aes(carat, price), data = diamonds) + 
  geom_point(alpha=0.5,size=3/4,position = "jitter") + 
  scale_x_continuous(trans = cuberoot_trans(), limits = c(0.2, 3),
                     breaks = c(0.2, 0.5, 1, 2, 3)) + 
  scale_y_continuous(trans = log10_trans(), limits = c(350, 15000),
                     breaks = c(350, 1000, 5000, 10000, 15000)) +
  ggtitle('Price (log10) by Cube-Root of Carat')

# 这样以后看到抖动后聚集的店就是明显的比较多的地方了嘛

```


```{r Overplotting Revisited}
ggplot(aes(carat, price), data = diamonds) + 
  geom_point() + 
  scale_x_continuous(trans = cuberoot_trans(), limits = c(0.2, 3),
                     breaks = c(0.2, 0.5, 1, 2, 3)) + 
  scale_y_continuous(trans = log10_trans(), limits = c(350, 15000),
                     breaks = c(350, 1000, 5000, 10000, 15000)) +
  ggtitle('Price (log10) by Cube-Root of Carat')
```

***

### Other Qualitative Factors
Notes:
12 定性因子的绘制颜色。
***

### Price vs. Carat and Clarity

Alter the code below.
```{r Price vs. Carat and Clarity}
# install and load the RColorBrewer package
install.packages('RColorBrewer')
library(RColorBrewer)


#我看不懂这个函数的式子，需要先看看。
cuberoot_trans = function() trans_new('cuberoot', transform = function(x) x^(1/3),
                                      inverse = function(x) x^3)


ggplot(aes(x = carat, y = price), data = diamonds) + 
  geom_point(alpha = 0.5, size = 1, position = 'jitter') +
  scale_color_brewer(type = 'div',
    guide = guide_legend(title = 'Clarity', reverse = T,
    override.aes = list(alpha = 1, size = 2))) +  
  scale_x_continuous(trans = cuberoot_trans(), limits = c(0.2, 3),
    breaks = c(0.2, 0.5, 1, 2, 3)) + 
  scale_y_continuous(trans = log10_trans(), limits = c(350, 15000),
    breaks = c(350, 1000, 5000, 10000, 15000)) +
  ggtitle('Price (log10) by Cube-Root of Carat and Clarity')



ggplot(aes(x = carat, y = price), data = diamonds) + 
  geom_point(alpha = 0.5, size = 1, position = 'jitter') +
  scale_color_brewer(type = 'div',
    guide = guide_legend(title = 'Clarity', reverse = T,
    override.aes = list(alpha = 1, size = 2))) +  
  scale_x_continuous(trans = cuberoot_trans(), limits = c(0.2, 3),
    breaks = c(0.2, 0.5, 1, 2, 3)) + 
  scale_y_continuous(trans = log10_trans(), limits = c(350, 15000),
    breaks = c(350, 1000, 5000, 10000, 15000)) +
  ggtitle('Price (log10) by Cube-Root of Carat and Clarity')
```

***

### Clarity and Price
Response:

***

### Price vs. Carat and Cut
15 价值和克拉的切工
Alter the code below.
```{r Price vs. Carat and Cut}
# 还需要设置size这个大小的东西。
# 映射的东西ggplot2中也是可以使用的，还可以在geom_point中进行显示，这两个都是可以的。

ggplot(aes(x = carat, y = price, color = cut), data = diamonds) + 
  geom_point(alpha = 0.5, size = 1, position = 'jitter') +
  scale_color_brewer(type = 'div',
                     guide = guide_legend(title = 'cut', reverse = T,
                                          override.aes = list(alpha = 1, size = 2))) +  
  scale_x_continuous(trans = cuberoot_trans(), limits = c(0.2, 3),
                     breaks = c(0.2, 0.5, 1, 2, 3)) + 
  scale_y_continuous(trans = log10_trans(), limits = c(350, 15000),
                     breaks = c(350, 1000, 5000, 10000, 15000)) +
  ggtitle('Price (log10) by Cube-Root of Carat and Clarity')
```

***
16 切割于价格，这个怎么回事。
### Cut and Price
Response:

***

### Price vs. Carat and Color
17 价值，与克拉 和颜色。
Alter the code below. 我从刚才开始都没有修改下面设置的标题。
```{r Price vs. Carat and Color}


# 颜色可以直接在ggplot内添加映射，也可以在后面geom_point中添加映射。
ggplot(aes(x = carat, y = price), data = diamonds) + 
  geom_point(alpha = 0.5, size = 1, position = 'jitter',aes(color=color)) +
  scale_color_brewer(type = 'div',
                     #颜色类型
                     # 小提示的标题
    guide = guide_legend(title = 'Clarity', reverse = T,
    override.aes = list(alpha = 1, size = 2))) +  
  
  # 设置刻度
  scale_x_continuous(trans = cuberoot_trans(), limits = c(0.2, 3),
    breaks = c(0.2, 0.5, 1, 2, 3)) + 
  scale_y_continuous(trans = log10_trans(), limits = c(350, 15000),
    breaks = c(350, 1000, 5000, 10000, 15000)) +
  
  # 图案的标题
  ggtitle('Price (log10) by Cube-Root of Carat and Clarity')



```




***
18 颜色与价格。
### Color and Price
Response:

***
19 R中的线性回归。
### Linear Models in R
Notes:
  这儿开始以后就是讲线性模型，这儿开始以后就好像不太懂了。
Response:
这儿意思就是必须要使用原来图形看起来就是线性那个来进行测试，进行学习。

***

### Building the Linear Model
Notes:

```{r Building the Linear Model}
m1 <- lm(I(log(price)) ~ I(carat^(1/3)), data = diamonds)
m2 <- update(m1, ~ . + carat)
m3 <- update(m2, ~ . + cut)
m4 <- update(m3, ~ . + color)
m5 <- update(m4, ~ . + clarity)
mtable(m1, m2, m3, m4, m5)
```

Notice how adding cut to our model does not help explain much of the variance
in the price of diamonds. This fits with out exploration earlier.

***

### Model Problems
Video Notes:

Research:
(Take some time to come up with 2-4 problems for the model)
(You should 10-20 min on this)

Response:

***

### A Bigger, Better Data Set
Notes:

```{r A Bigger, Better Data Set}
install.package('bitops')
install.packages('RCurl')
library('bitops')
library('RCurl')

diamondsurl = getBinaryURL("https://raw.github.com/solomonm/diamonds-data/master/BigDiamonds.Rda")
load(rawConnection(diamondsurl))
```

The code used to obtain the data is available here:
https://github.com/solomonm/diamonds-data

## Building a Model Using the Big Diamonds Data Set
Notes:

```{r Building a Model Using the Big Diamonds Data Set}

```


***

## Predictions

Example Diamond from BlueNile:
Round 1.00 Very Good I VS1 $5,601

```{r}
#Be sure you’ve loaded the library memisc and have m5 saved as an object in your workspace.
thisDiamond = data.frame(carat = 1.00, cut = "V.Good",
                         color = "I", clarity="VS1")
modelEstimate = predict(m5, newdata = thisDiamond,
                        interval="prediction", level = .95)
```

Evaluate how well the model predicts the BlueNile diamond's price. Think about the fitted point estimate as well as the 95% CI.

***

## Final Thoughts
Notes:

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!

